Multi-reference pangenome graphs

### 2022-01-05 manuscript/fig_induction.tex
smaller key

\begin{document}
\begin{tikzpicture}[auto,
    node distance= 10mm and 20mm,
    roundnode/.style={circle, draw=black!60, fill=gray!10, very thick, minimum size=7mm},
    squarednode/.style={rectangle, draw=black!60, fill=gray!10, very thick, minimum size=5mm},
]
%Nodes
\node[squarednode] (seqA1) {G};
\node[squarednode] (seqA2) [right of=seqA1] {A};
\node[squarednode] (seqA3) [right of=seqA2] {T};
\node[squarednode] (seqA4) [right of=seqA3] {T};
\node[squarednode] (seqA5) [right of=seqA4] {A};
\node[squarednode] (seqA6) [right of=seqA5] {C};
\node[squarednode] (seqA7) [right of=seqA6] {A};

@@

\begin{scope}[node distance=0.5cm]
  \node[squarednode,fill=red!100] (c1) [right = 1cm of seqA7] {1};
  \node[squarednode,fill={rgb:red,1;orange,1}] (c2) [below of=c1] {2};
  \node[squarednode,fill=orange!100] (c3) [below of=c2] {3};
  \node[squarednode,fill=green!100] (c4) [below of=c3] {4};
  \node[squarednode,fill={rgb:blue,1;green,1},text=white] (c5) [below of=c4] {5};
  \node[squarednode,fill=blue!100,text=white] (c6) [below of=c5] {6};
  \node[squarednode,fill={rgb:blue,1;purple,1},text=white] (c7) [below of=c6] {7};
  \node[squarednode,fill=purple!100] (c8) [below of=c7] {8};
  \node[squarednode,fill=gray] (c9) [below of=c8] {9};
\end{scope}

>>>>

\begin{document}
\begin{tikzpicture}[auto,
    node distance= 10mm and 20mm,
    roundnode/.style={circle, draw=black!60, fill=gray!10, very thick, minimum size=7mm},
    squarednode/.style={rectangle, draw=black!60, fill=gray!10, very thick, minimum size=5mm},
    keynode/.style={rectangle, draw=black!60, fill=gray!10, thick, minimum size=1mm}
]
%Nodes
\node[squarednode] (seqA1) {G};
\node[squarednode] (seqA2) [right of=seqA1] {A};
\node[squarednode] (seqA3) [right of=seqA2] {T};
\node[squarednode] (seqA4) [right of=seqA3] {T};
\node[squarednode] (seqA5) [right of=seqA4] {A};
\node[squarednode] (seqA6) [right of=seqA5] {C};
\node[squarednode] (seqA7) [right of=seqA6] {A};

@@

\begin{scope}[node distance=0.5cm]
  \node[keynode,fill=red!100] (c1) [right = 1cm of seqA7] {1};
  \node[keynode,fill={rgb:red,1;orange,1}] (c2) [below of=c1] {2};
  \node[keynode,fill=orange!100] (c3) [below of=c2] {3};
  \node[keynode,fill=green!100] (c4) [below of=c3] {4};
  \node[keynode,fill={rgb:blue,1;green,1},text=white] (c5) [below of=c4] {5};
  \node[keynode,fill=blue!100,text=white] (c6) [below of=c5] {6};
  \node[keynode,fill={rgb:blue,1;purple,1},text=white] (c7) [below of=c6] {7};
  \node[keynode,fill=purple!100] (c8) [below of=c7] {8};
  \node[keynode,fill=gray] (c9) [below of=c8] {9};
\end{scope}
